---
title: "STAT345_Midterm_Code"
author: "Kayleigh Baasch"
date: "2023-03-31"
output: word_document
---
Note that the following is only the code used to make this midterm project. Throughout the code there are also explanations associated with certain parts of the code. The code has been split into multiple sections

## All Libraries Used
```{r}
#Sys.setenv(VROOM_CONNECTION_SIZE = 500000)

library(tidyverse)
library(ggplot2)
library(nbastatR)
library(gganimate)
library(gifski)
library(transformr)
library(magick)
```

## Creating the Court
```{r}
#The following code is used to create the court plot and draw the lines on the court. Note that this code comes before the shot data to allow for the data to be scaled to specific elements within the code in this section

#Creating the court (original code from - https://www.owenlhjphillips.com/new-blog/2020/6/25/how-to-make-nba-shots-charts-in-r)
#Note that 'court_theme' and the legend has been edited from the original code

  #The court
circle_points = function(center = c(0, 0), radius = 1, npoints = 360) {
  angles = seq(0, 2 * pi, length.out = npoints)
  return(data_frame(x = center[1] + radius * cos(angles),
                    y = center[2] + radius * sin(angles)))
}

  #Lines and dimensions
width = 50
height = 94 / 2
key_height = 19
inner_key_width = 12
outer_key_width = 16
backboard_width = 6
backboard_offset = 4
neck_length = 0.5
hoop_radius = 0.75
hoop_center_y = backboard_offset + neck_length + hoop_radius
three_point_radius = 23.75
three_point_side_radius = 22
three_point_side_height = 14

  #Colors for the plot
    #note that the 'court' hexcode has been edited from the orginal code and that the 'light' court_theme has been removed entirely
court_themes = list(
  dark = list(
    court = '#9E998E',
    lines = '#000000',
    text = '#000000',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 0,
    hex_border_color = "#000000"
  )
)

  #The function to make the court
plot_court = function(court_theme = court_themes$light, use_short_three = FALSE) {
  if (use_short_three) {
    three_point_radius = 22
    three_point_side_height = 0
  }
  
  court_points = data_frame(
    x = c(width / 2, width / 2, -width / 2, -width / 2, width / 2),
    y = c(height, 0, 0, height, height),
    desc = "perimeter"
  )
  
  court_points = bind_rows(court_points , data_frame(
    x = c(outer_key_width / 2, outer_key_width / 2, -outer_key_width / 2, -outer_key_width / 2),
    y = c(0, key_height, key_height, 0),
    desc = "outer_key"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(-backboard_width / 2, backboard_width / 2),
    y = c(backboard_offset, backboard_offset),
    desc = "backboard"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(0, 0), y = c(backboard_offset, backboard_offset + neck_length), desc = "neck"
  ))
  
  foul_circle = circle_points(center = c(0, key_height), radius = inner_key_width / 2)
  
  foul_circle_top = filter(foul_circle, y > key_height) %>%
    mutate(desc = "foul_circle_top")
  
  foul_circle_bottom = filter(foul_circle, y < key_height) %>%
    mutate(
      angle = atan((y - key_height) / x) * 180 / pi,
      angle_group = floor((angle - 5.625) / 11.25),
      desc = paste0("foul_circle_bottom_", angle_group)
    ) %>%
    filter(angle_group %% 2 == 0) %>%
    select(x, y, desc)
  
  hoop = circle_points(center = c(0, hoop_center_y), radius = hoop_radius) %>%
    mutate(desc = "hoop")
  
  restricted = circle_points(center = c(0, hoop_center_y), radius = 4) %>%
    filter(y >= hoop_center_y) %>%
    mutate(desc = "restricted")
  
  three_point_circle = circle_points(center = c(0, hoop_center_y), radius = three_point_radius) %>%
    filter(y >= three_point_side_height, y >= hoop_center_y)
  
  three_point_line = data_frame(
    x = c(three_point_side_radius, three_point_side_radius, three_point_circle$x, -three_point_side_radius, -three_point_side_radius),
    y = c(0, three_point_side_height, three_point_circle$y, three_point_side_height, 0),
    desc = "three_point_line"
  )
  
  court_points = bind_rows(
    court_points,
    foul_circle_top,
    foul_circle_bottom,
    hoop,
    restricted,
    three_point_line
  )
  
  
  court_points <- court_points
  

  #The plot and legend (edited)
    #note that the 'fill' color has been in 'plot.background' has been edited from the original code
ggplot() +
    geom_path(
      data = court_points,
      aes(x = x, y = y, group = desc),
      color = court_theme$lines
    ) +
    coord_fixed(ylim = c(0, 45), xlim = c(-25, 25)) +
    theme_minimal(base_size = 14) +
    theme(
      text = element_text(color = court_theme$text),
      plot.background = element_rect(fill = 'white', color = ' white'),
      panel.background = element_rect(fill = court_theme$court, color = court_theme$court),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
    )
}
```

## Pulling the Milwaukee Bucks Seasons Shot Charts
```{r}
#Pulling the data from 'teams_shots' 
#Making every year of data into an object and scaling the data to fit on the court when plotting
#Note that each season/year's data has been scaled to fit the court from the prior code

Bucks_shots_2020 <- teams_shots(teams = "Bucks", seasons = 2020) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2019 <- teams_shots(teams = "Bucks", seasons = 2019) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2018 <- teams_shots(teams = "Bucks", seasons = 2018) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2017 <- teams_shots(teams = "Bucks", seasons = 2017) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2016 <- teams_shots(teams = "Bucks", seasons = 2016) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2015 <- teams_shots(teams = "Bucks", seasons = 2015) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2014 <- teams_shots(teams = "Bucks", seasons = 2014) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2013 <- teams_shots(teams = "Bucks", seasons = 2013) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2012 <- teams_shots(teams = "Bucks", seasons = 2012) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2011 <- teams_shots(teams = "Bucks", seasons = 2011) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2010 <- teams_shots(teams = "Bucks", seasons = 2010) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2009 <- teams_shots(teams = "Bucks", seasons = 2009) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2008 <- teams_shots(teams = "Bucks", seasons = 2008) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2007 <- teams_shots(teams = "Bucks", seasons = 2007) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2006 <- teams_shots(teams = "Bucks", seasons = 2006) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2005 <- teams_shots(teams = "Bucks", seasons = 2005) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2004 <- teams_shots(teams = "Bucks", seasons = 2004) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2003 <- teams_shots(teams = "Bucks", seasons = 2003) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2002 <- teams_shots(teams = "Bucks", seasons = 2002) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2001 <- teams_shots(teams = "Bucks", seasons = 2001) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_2000 <- teams_shots(teams = "Bucks", seasons = 2000) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_1999 <- teams_shots(teams = "Bucks", seasons = 1999) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_1998 <- teams_shots(teams = "Bucks", seasons = 1998) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)
Bucks_shots_1997 <- teams_shots(teams = "Bucks", seasons = 1997) %>% mutate(x = as.numeric(as.character(locationX)) / 10, y = as.numeric(as.character(locationY)) / 10 + hoop_center_y)



#Creating a list of all the years of shot data for the Bucks

Bucks_shots <- list(Bucks_shots_1997, Bucks_shots_1998, Bucks_shots_1999, Bucks_shots_2000, Bucks_shots_2001, Bucks_shots_2002, Bucks_shots_2003, Bucks_shots_2004, Bucks_shots_2005, Bucks_shots_2006, Bucks_shots_2007, Bucks_shots_2008, Bucks_shots_2009, Bucks_shots_2010, Bucks_shots_2011, Bucks_shots_2012, Bucks_shots_2013, Bucks_shots_2014, Bucks_shots_2015, Bucks_shots_2016, Bucks_shots_2017, Bucks_shots_2018, Bucks_shots_2019, Bucks_shots_2020)



#Binding all rows in the list

Bucks_shots <-bind_rows(Bucks_shots)
```

## All Color Themes Created
```{r}
#A new color theme using the Bucks colors
#Note that 'bucks_colors_more' and 'bucks_colors_moremore' have just extended the repeated pattern shown in 'bucks_colors'
bucks_colors <- c("#EEE1C6", "#00471B")

bucks_colors_more <- c("#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B")

bucks_colors_moremore <- c("#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B","#EEE1C6", "#00471B")
```

## Creating and Animating the Half-Court Graphic With 1997-2020 Milwuakee Bucks Seasons Shots Data

  This animation displays each of the years' shot data from the Bucks from 1997-2020. From the graphic we can see where each shot was taken on the court, but it is somewhat difficult to compare the amount of "Missed" shots to "Made" shots.
  It should also be noted that each 'Year' that is shown in the graphic represents a season. 
    i.e. The 2019-20 season is equivilant to 'Year: 2020', 2018-19 to 'Year: 2019', etc.
  Each season will from now on be refered to as a year.
  
```{r}
#The animated ggplot using all years of data
#Note that...
  #in 'animate()', 'nframes = 24' was used to show only one plot for each year in the data
  #when making the subtitle of the plot, 'Year: {as.integer(frame_time)}' was used to show the numerical values of each year as integers rather than doubles
  #'fps = 0.75' was used to create a slower transition between years/plots

Bucks_Shots_Animated <- plot_court(court_themes$dark, use_short_three = F) + 
  geom_point(data = Bucks_shots, aes(x = x, y = y, color = isShotMade), size = 1.5, alpha = 0.5) +
  xlab("") +
  ylab("") +
  ggtitle("Shots Attempted by the Milwaukee Bucks") +
  scale_color_manual(values=bucks_colors, 
                     name = "Shots Attempted",
                     labels = c( "TRUE" = "Made", 
                                 "FALSE" = "Missed"
              )) +
  transition_time(yearSeason) +
  labs(title = "Shots Attempted by the Milwaukee Bucks -",
       subtitle = "Year: {as.integer(frame_time)}")

animate(Bucks_Shots_Animated, fps = 0.75, nframes = 24)
```
  
## Creating and Animating the Bar Graph Graphic with 1997-2020 Milwaukee Bucks Seasons Shots Data

  This animation displays each year's shot data from the previous graphic as a bar graph. This graph may be easier to interpret than the Court graph when trying to comparing how many shots were "Missed" or "Made".

```{r}
#An animated plot showing the amount of shots that were made and missed each year in a more understandable graphic
#Note that...
  #in 'animate()', 'nframes = 24' was used to show only one plot for each year in the data
  #when making the subtitle of the plot, 'Year: {as.integer(frame_time)}' was used to show the numerical values of each year as integers rather than doubles
  #'fps = 0.75' was used to create a slower transition between years/plots
  
mandm_labels_xaxis <- c("Missed", "Made") 
  
Bucks_shots_mandm_amounts <- Bucks_shots %>% 
  ggplot(aes(x=isShotMade, fill = isShotMade)) +
  geom_bar() +
  scale_fill_manual(values = bucks_colors, 
                     name = "Shots Attempted",
                     labels = c( "TRUE" = "Made", 
                                 "FALSE" = "Missed"
              )) +
  ylab("Amount of Shots") +
  xlab("Shot Type") +
  ggtitle("Shots Attempted by the Milwaukee Bucks") +
  scale_x_discrete(labels = mandm_labels_xaxis) +
  theme(panel.background = element_rect(fill = "#9E998E")) + 
  transition_time(yearSeason)+
  labs(title = "Shots Attempted by the Milwaukee Bucks -", 
       subtitle = "Year: {as.integer(frame_time)}")

animate(Bucks_shots_mandm_amounts, fps = 0.75, nframes = 24)
```

## Combining the Animated Half-Court and Bar Graph Graphics

  The following code puts the two previous animations together into a single graphic. The two graphs will be displayed side by side to allow for easier analysis of where shots were made, whether they were a "Made" or "Missed" shot, and how many "Made" and "Missed" shots there were each year. 
  
```{r}
#Putting the two graphics side-by-side
#'image_append' was using to make the graphics into a single GIF where the graphics are side by side
  #this allows both graphics to be paused and restarted at the same time after knitting

Bucks_shots_gif <- animate(Bucks_Shots_Animated, fps = 0.75, nframes = 24)
Bucks_mandm_shots_gif <- animate(Bucks_shots_mandm_amounts, fps = 0.75, nframes = 24)

Bucks_shots_gif <- image_read(Bucks_shots_gif)
Bucks_mandm_shots_gif <- image_read(Bucks_mandm_shots_gif)


Bucks_shots_and_MadeandMissed_shots_gif <- image_append(c(Bucks_shots_gif[1], Bucks_mandm_shots_gif[1]))

for(i in 2:24){
  combined <- image_append(c(Bucks_shots_gif[i], Bucks_mandm_shots_gif[i]))
  Bucks_shots_and_MadeandMissed_shots_gif <- c(Bucks_shots_and_MadeandMissed_shots_gif, combined)
}

Bucks_shots_and_MadeandMissed_shots_gif
```

## Pulling the Milwuakee Bucks Yearly Performance
```{r}
#Pulling the data for the Bucks yearly performance from 1997-2020 from 'teams_annual_stats'

teams_annual_stats(teams = "Bucks", season_types = c("Regular Season"), modes = c("Totals"), return_message = TRUE, nest_data = F)

Bucks_Annual_Stats <- (teams_annual_stats(teams = "Bucks", season_types = c("Regular Season"), modes = c("Totals"), return_message = TRUE, nest_data = F) 
                       %>% filter(nameTeam == "Milwaukee Bucks")
                       %>% filter(slugSeason %in% c('1996-97', '1997-98', '1998-99', '1999-00', '2000-01', '2001-02', '2002-03', '2003-04', '2004-05', '2005-06', '2006-07', '2007-08', '2008-09', '2009-10', '2010-11', '2011-12', '2012-13', '2013-14', '2014-15', '2015-16', '2016-17', '2017-18', '2018-19', '2019-20')))


#Renaming the seasons to a single value representing a year

Bucks_Annual_Stats[Bucks_Annual_Stats == "1996-97"] <- "1997"
Bucks_Annual_Stats[Bucks_Annual_Stats == "1997-98"] <- "1998"
Bucks_Annual_Stats[Bucks_Annual_Stats == "1998-99"] <- "1999"
Bucks_Annual_Stats[Bucks_Annual_Stats == "1999-00"] <- "2000"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2000-01"] <- "2001"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2001-02"] <- "2002"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2002-03"] <- "2003"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2003-04"] <- "2004"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2004-05"] <- "2005"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2005-06"] <- "2006"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2006-07"] <- "2007"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2007-08"] <- "2008"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2008-09"] <- "2009"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2009-10"] <- "2010"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2010-11"] <- "2011"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2011-12"] <- "2012"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2012-13"] <- "2013"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2013-14"] <- "2014"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2014-15"] <- "2015"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2015-16"] <- "2016"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2016-17"] <- "2017"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2017-18"] <- "2018"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2018-19"] <- "2019"
Bucks_Annual_Stats[Bucks_Annual_Stats == "2019-20"] <- "2020"


#Transforming the renamed year values into integers

Bucks_Annual_Stats_edited <- transform(Bucks_Annual_Stats, slugSeason = as.integer(slugSeason))
```

## Creating and Animating a Graphic of the Milwaukee Bucks Total Points from 1997-2020

  The following animation shows the total points made each year by the Bucks. The colors alteranate and the bar shifts to the right with each subsequent year to help distinguish when the graph moves to the next year. 
  
```{r}
#Note that...
  #in 'animate()', 'nframes = 24' was used to show only one plot for each year in the data
  #when making the subtitle of the plot, 'Year: {as.integer(frame_time)}' was used to show the numerical values of each year as integers rather than doubles
  #'fps = 0.75' was used to create a slower transition between years/plots
  
Bucks_Points <- Bucks_Annual_Stats_edited %>%
  ggplot(aes(x = slugSeason, y = pts, fill = factor(slugSeason))) +
  geom_col() +
  theme(axis.text.x=element_text(color = "black", size=11, angle=70, vjust=.8, hjust=0.8)) +
  scale_fill_manual(values=bucks_colors_more) +
  theme(panel.background = element_rect(fill = "#9E998E")) +
  xlab("Season") +
  ylab("Points") +
  ggtitle("Points Made by the Milwaukee Bucks") +
  theme(legend.position= "none") +
  transition_time(slugSeason) +
  labs(title = "Points Made by the Milwaukee Bucks -",
      subtitle = "Year: {as.integer(frame_time)}")

animate(Bucks_Points, fps = 0.75, nframes = 24)
```

## Filtering the Bucks' Shots for Only "Made" Shots
```{r}
Bucks_shots_filtered <- filter(Bucks_shots, typeEvent == "Made Shot")
Bucks_shots_filtered
```

## Creating and Animating a Graphic of all "Two-Point" and "Three-Point" from "Made" Shots by the Bucks each Season
  
  The following animation shows the total amount of "Two-point" and "Three-Point" shots made by the Bucks each season. Note that all data representing "Missing" shots has been filtered out so only "Made" shots are represented in this graphic so we can compare the amount of successful "Two-Point" and "Three-Point" shots. This will be built upon in a later graphic showing a comparision of successful shot types that have been further broken down.
  
```{r}
##Note that...
  #in 'animate()', 'nframes = 24' was used to show only one plot for each year in the data
  #when making the subtitle of the plot, 'Year: {as.integer(frame_time)}' was used to show the numerical values of each year as integers rather than doubles
  #'fps = 0.75' was used to create a slower transition between years/plots
  #'\' followed by 'enter'-ing to a new line of code in the title of plot put the title on two lines to prevent any words form being cut off
  
Bucks_twopoint_threepoint <- Bucks_shots_filtered %>% 
  ggplot(aes(x=typeShot, fill = typeShot)) +
  geom_bar() +
  scale_fill_manual(values = bucks_colors, 
                     name = "Shot Type",
                     labels = c( "2PT Field Goal" = "Two-Point",
                                 "3PT Field Goal" = "Three-Point")) +
  ylab("Amount") +
  xlab("Shot Type") +
  scale_x_discrete(labels = twopoint_threepoint) +
  theme(panel.background = element_rect(fill = "#9E998E")) + 
  transition_time(yearSeason)+
  labs(title = "Two- and Three-Point Shots Made \ 
       by the Milwaukee Bucks -",
       subtitle = "Year: {as.integer(frame_time)}")

animate(Bucks_twopoint_threepoint, fps = 0.75, nframe = 24)
```

## Creating and Animating a Graphic of all the Shot Types from "Made" Shots by the Bucks each Season 
  
  The following animation shows a comparision of the amount of each type of shot was successfully made each season. In the animation, the bars aleternate colors to help viewers distinguish between the different bars and shot types. Note that this data only represents "Made" shots and that all "Missing" shots have been filtered out. To reiterate, this graphic does not show the total amount of each shot type attempted, it only shows the amount of each shot type that was successfuly "Made."
  
```{r}
##Note that...
  #in 'animate()', 'nframes = 24' was used to show only one plot for each year in the data
  #when making the subtitle of the plot, 'Year: {as.integer(frame_time)}' was used to show the numerical values of each year as integers rather than doubles
  #'fps = 0.75' was used to create a slower transition between years/plots
  #'\' followed by 'enter'-ing to a new line of code in the title of plot put the title on two lines to prevent any words form being cut off
  
Bucks_Seasons_Shots_Types <- Bucks_shots_filtered %>% 
  ggplot(aes(x = typeAction, y = typeEvent, fill = factor(typeAction))) + 
  geom_col() +
  theme(axis.text.x=element_text(color = "black", size=6, angle=90, vjust=0, hjust=0.8)) +
  xlab("Shot Type") +
  ylab(" ") +
  scale_fill_manual(values=bucks_colors_moremore) +
  theme(legend.position= "none") +
  theme(panel.background = element_rect(fill = "#9E998E")) +
    transition_time(yearSeason) +
  labs(title = "Proportion of Shot Types Made \
       by the Milwaukee Bucks -",
       subtitle = "Year: {as.integer(frame_time)}")

animate(Bucks_Seasons_Shots_Types, fps = 0.75, nframe = 24)
```

## Making GIFs and Combining Two of the Graphics

  The following code either (1) puts the first two of the the previous three animations together into a single graphic, followed by the the third graphic, or (2) combines all three animations into a single graphic. 
  In (1), the combined graphic and third graphic will be displayed in two rows. This allows for the "Proportion of Shot Types Made by the Milwaukee Bucks" graphic to be displayed larger.
  In (2), the combined graphic of all three animations will be displayed in one row with three side-by-side animations.
  The two options provided allow for the user to decide how they would like to display the data and graphics.


```{r}
#'image_append' was using to make the graphics into a single GIF where the graphics are side by side
  #this allows both graphics to be paused and restarted at the same time after knitting
#note that 'Bucks_Seasons_ShotType_gif' was not used in the 'image_append()' in 'BuckShots' to allow for the graphic to be made larger when knitting
  #should it be desired for 'Bucks_Seasons_ShotType_gif' to be added into the single GIF, use/run 'BuckShots_AllThree'

Bucks_points_gif <- animate(Bucks_Points, fps = 0.75, nframes = 24)
Bucks_Seasons_ShotTypes_gif <- animate(Bucks_Seasons_Shots_Types, fps = 0.75, nframe = 24)
Bucks_TwoThreePoints_gif <- animate(Bucks_twopoint_threepoint, fps = 0.75, nframe = 24)

Bucks_points_gif <- image_read(Bucks_points_gif)
Bucks_Seasons_ShotTypes_gif <- image_read(Bucks_Seasons_ShotTypes_gif)
Bucks_TwoThreePoints_gif <- image_read(Bucks_TwoThreePoints_gif)

 
BuckShots <- image_append(c(Bucks_points_gif[1], Bucks_TwoThreePoints_gif[1]))
for(i in 2:24){
  combined <- image_append(c(Bucks_points_gif[i], Bucks_TwoThreePoints_gif[i]))
  BuckShots <- c(BuckShots, combined)
}

BuckShots
Bucks_Seasons_ShotTypes_gif



BuckShots_AllThree <- image_append(c(Bucks_points_gif[1], Bucks_TwoThreePoints_gif[1], Bucks_Seasons_ShotTypes_gif[1]))
for(i in 2:24){
  combined <- image_append(c(Bucks_points_gif[i], Bucks_TwoThreePoints_gif[i], Bucks_Seasons_ShotTypes_gif[i]))
  BuckShots_AllThree <- c(BuckShots_AllThree, combined)
}

BuckShots_AllThree
```












